Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-04-29 paper/tidy-missing-data-paper.Rmd
overview of graphics

The  first step is to get an overview of the extent of the missingness. <!--Rather than highlighting the amount of complete data,-->  Overview visualisations for variables and cases are provided with `gg_miss_var` and `gg_miss_case` (Figure \@ref(fig:gg-miss-case-var)). These  missing data visualizations should draw attention to the amount of missings, and ordering by missingness. The "airquality" dataset (available in base R), included in base R, containing daily air quality measurements in New York, from May to September, 1973, is shown.

>>>>

The  first step is to get an overview of the extent of the missingness. <!--Rather than highlighting the amount of complete data,-->  Overview visualisations for variables and cases are provided with `gg_miss_var` and `gg_miss_case` (Figure \@ref(fig:gg-miss-case-var)). These  missing data visualizations should draw attention to the amount of missings, and ordering by missingness. The "airquality" dataset (available in base R), included in base R, containing daily air quality measurements in New York, from May to September, 1973, is shown. Two of the variables contain missings and about one third of observations have one missing value. A tiny number of observations are missing on two variables. These summary plots compute proportions from the shadow matrix. The numerical statistics can also be reported, and is discussed in the next section.
